Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
#pf <- read.csv('pseudo_facebook.tsv', sep="\t")
#names(pf)
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
#install.packages('ggplot2')
#library(ggplot2)
#qplot(x = dob_day, data = pf)

```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
 qplot(x = dob_day, data = pf) +
  scale_x_discrete(breaks = 1:31) +
  facet_wrap(~dob_month, ncol = 3)
```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
qplot(x = friend_count, data = pf) #+
  #scale_x_discrete(breaks = 1:10) #+
  #facet_wrap(~dob_month, ncol = 3)
```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
#qplot(x = friend_count, data = pf) +
#  scale_x_continuous(limits = c(1,1000))
# or 
qplot(x = friend_count, data = pf, xlim = c(0,1000))
```
Parameter für qplot:
`x = Variabelname`
`data = Datenname`
`xlim = Vektor(Von, Bis)`
`binwidth = Balkendicke`
`facet_wrap(~gender, ncol = 2) -- Aufteilen in Einzelne kleine Fenster`

### Exploring with Bin Width
Notes: qplot(x = friend_count, data = pf, xlim = c(0,500), binwidth = 5)

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.

qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))+
  facet_wrap(~gender, ncol = 2)
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
qplot(x = friend_count, data = subset(pf, !is.na(gender)), binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))+
  facet_wrap(~gender, ncol = 2)
```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
table(pf$gender)
by(pf,pf$gender, summary)

```

#### Who on average has more friends: men or women?
Response: women

#### What's the difference between the median friend count for women and men?
Response: 22

#### Why would the median be a better measure than the mean?
Response: roboust

***

### Tenure
Notes:

```{r Tenure}
qplot(x = tenure, data = pf, binwidt = 30, fill=I("green")) 
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(x = tenure/365, data = pf, binwidt = 1, fill=I("green")) + scale_x_continuous(breaks = seq(1, 7 ,1), lim = c(0, 7))
```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
qplot(x = tenure/365, data = pf, xlab = " Number of years", ylab = "Number of users", binwidt = 1, fill=I("green")) + scale_x_continuous(breaks = seq(1, 7 ,1), lim = c(0, 7))

```

***

### User Ages
Notes:

```{r User Ages}
qplot(x = age, data = pf, xlab = " age", ylab = "Number of users", binwidt = 1, fill=I("green")) + scale_x_continuous(breaks = seq(5, 100 ,5), lim = c(5, 100))
```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:
```{r eval=FALSE}
qplot(x = friend_count, data = pf)

summary(pf$friend_count)
summary(log10(pf$friend_count))
summary(log10(pf$friend_count+1))
summary(sqrt(pf$friend_count))

```

***
Um mehrere Graphen in einer Darstellung zu haben, gibt es das Packet **gridExtra**
```{r}
install.packages("gridExtra")
```
Generate individual plots and arrange in grid
```{r}
# define individual plots
p1 = qplot(x = friend_count, data = pf)
p2 = qplot(x = age, data = pf, xlab = " age", ylab = "Number of users", binwidt = 1, fill=I("green"))
p3 = qplot(x = tenure/365, data = pf, xlab = " Number of years", ylab = "Number of users", binwidt = 1, fill=I("green"))
# arrange plots in grid
grid.arrange(p1, p2, p3, ncol=2)
# See more at: http://lightonphiri.org/blog/ggplot2-multiple-plots-in-one-graph-using-gridextra#sthash.uNm3sOO5.dpuf

```


### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}

```

***


### Frequency Polygons

```{r Frequency Polygons}

```

***

### Likes on the Web
Notes:

```{r Likes on the Web}

```


***

### Box Plots
Notes:

```{r Box Plots}

```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}

```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}

```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}

```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!